Generality in food webs scales with species richness, not latitude

### 2015-05-18 manuscript/latitudepaper.tex
I can has conclusions

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships in the estuarine,
marine, and terrestrial food webs, there were strong effects of latitude on
scaling relationships in the freshwater food webs. [[Need MUCH stronger justification for these... In lakes, this trend is
driven by increasing generality in high-latitude top predators while in
streams this trend appears to be driven by greater proportions of basal
resources in polar communities. Our results therefore provide partial support
the latitude-niche breadth hypothesis but also suggest that it may have
limited applicability in many empirical ecosystems. ]]

\section*{Introduction} [[Add something about ecosystem type since it's in the methods]]

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities \citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
  such as habitat type \citep{Shurin2006,Briand1983}, primary productivity \citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes \citep{mappaper}. These variables affect both the resources available and species' 
  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.

@@

  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{,Vazquez2004}. 
  This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
  turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
  coexist in the tropics than at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
  may result in a broader niche space \citep{Davies2007} which could also allow greater diversification even if niche 
  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocably 
  supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
  richness \citep{Lappalainen2006,Krasnov2008,Slove2010}.

  If decreased seasonality or higher productivity is the cause of higher species-richness in the tropics, then 
  there should be other effects of latitudinal gradients on food-web structure. Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. In particular,
  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
  the ``latitude-niche breadth hypothesis''.

@@

  As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
  is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
  Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
  sets to form ``trophic species'' webs (e.g. ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
  is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
  species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
  of the dataset; in each case using the number of species ($S$) and 
  links ($L$) in each web to calculate the mean number of links per species ($Z$), mean generality 
  ($G$), and mean vulnerability ($V$) of the web. 
  The version of the dataset used did not qualitatively change the results, suggesting that
  the scaling relationships between species richness, other food-web properties, and latitude are very 
  similar whether or not redundant species are included. For simplicity, we present only
  the results for the original webs in the main text.

@@

  To determine whether there were latitudinal gradients in food-web structure,
  we first examined simple linear relationships between latitude and each of 
  $S$, $Z$, $G$, $V$, $B$, $I$, and $T$. We fit models of the form

@@

  \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
  latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
  variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
  marine, lake, and terrestrial networks with estuarine
  networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
  We next calculated the AIC
  of the maximal model, as well as the AIC's of a suite of candidate simplified models identified
  using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
  Simplified models were obtained by
  systematically removing all possible combinations of terms from the full model.
  The best-fitting model was then determined to be the model with the fewest terms 
  where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
  and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
  model.

@@

  Next, we examined the form of the scaling relationship between each 
  property ($Z$, $G$, and $V$) and $S$. The scaling relationship between $Z$ and 
  $S$ has been shown to be a power law \citep{Riede2010} of the form

@@

  Although scaling relationships between $S$ and $G$ or $S$ and $V$ have not been explicitly examined (but see scaling 
  relationships for the standard devaitions of each property in \citet{Riede2010}), we expect that they will follow
  power laws similar to that of the relationship between $S$ and $Z$. This is because the links taken into account in
  calculating $G$ and $V$ are subsets of the total links included when calculating $Z$. As with $Z$, we explicitly 
  compared the error distributions of models for $G$ and $V$ using both the power-law and logarithmic formulations. 
  In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
  species richness.

@@

  We then assessed the impact of latitude on the scaling relationships between species richness and 
  link density, generality, vulnerability.
  [[If the species-rich tropics truly have narrower 
  niches~\citep{Brown2004}, then we would expect to see less increase in mean numbers of links, 
  predators, and prey with increasing species richness in the tropics. ]]
  In the context of the scaling relationships above, note that this implies that we aim to determine the effect of latitude on
  the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
  web property directly, we included a categorical variable for ecosystem type (stream, lake, 
  terrestrial, marine, or estuary), as well as interactions between food web type and latitude.

@@

  We were also interested in the ways that scaling relationships with species richness might
  be affected by changes to the distribution of species among trophic levels. To
  that end, we repeated all of the above analyses replacing species richness by
  proportion of basal resources $B$, proportion of intermediate consumers $I$,
  or proportion of top predators $T$. All model fitting and model
  simplification procedures were identical to those described for species
  richness.

@@

  Contrary to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
  ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
  relationship was robust to the removal of three outliers (based on Cook's Distance). In the best-fit versions of
  equation~(\ref{Latfull}) for link density and vulnerability, there were once again
  significant relationships with latitude in stream food webs, but after the removal of three outliers these trends
  were no longer significant. Link density and vulnerability did not vary with latitude in any other ecosystem type.
  Similarly, the best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
  latitude in any ecosystem type.

  The relationships between the proportions of species at each trophic level with latitude were broadly similar
  to the relationship between species richness and latitude. 
  The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
  but did not vary with latitude in estuarine, marine, lake, or terrestrial 
  food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
  The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
  The proportion of top predators did not vary with latitude in 
  estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
  webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
  $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
  All of these trends were robust to the removal of outliers.

@@

  When considering the relationships between species richness and proportions 
  of basal resources, intermediate consumers, and top predators and all response variables 
  (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
  lower AIC than did equation~(\ref{Power}). This indicates that the
  data support an assumption of multiplicative lognormal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an additive term on
  the logarithmic scale provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with species richness.

@@

Link density, generality, and vulnerability each increased with increasing
species richness (Fig.~\ref{S}; $\beta_0$=0.666, $p$\textless0.001; $\beta_0$=0.623,
$p$\textless0.001; and $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine,
marine, and terrestrial food webs this increase did not vary with latitude
($\beta_{Latitude}$=-0.001, $p$=0.267 for link density; $\beta_{Latitude}$=-0.001, $p$=0.363 for generality;
and $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability). In lake food webs, link density,
generality, and vulnerability all increased more quickly towards the poles
($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
stream food webs generality increased more rapidly towards the poles 
($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.

@@

The tendency of food-web structure to exhibit scaling relationships with
species richness has been well-established \citep{Dunne2004,Riede2010}. As
species richness in particular is also known to vary systematically over
latitude \citep{}, intuitively one might suspect that any relationship
between food-web properties such as generality might be due to the latitudinal
gradient in species richness. In this dataset, however, we did not find
overall latitudinal gradients in species richness, links per species, 
generality, vulnerability, or the proportions of food webs accounted for by 
basal resources, intermediate consumers, and top predators.

The lack of latitudinal gradients in food-web properties in this dataset contrasts
strongly with other studies which have found consistent variation in species richness,
[[other properties]] \citep{}. As numbers of species and links included in a food web
vary strongly with sampling effort as well as with the underlying diversity of the study
area, it is possible that the lack of latitudinal trends here is a result of researchers
tending to expend similar amounts of sampling effort across studies. This could result in
food webs describing species-rich tropical communities omitting more species and links
than species-poor arctic communities. In addition, it is worth noting that gradients in
species richness are generally measured for a single taxonomic group at a time~\citep{}.
It is possible that these taxa are not well-represented in our food webs and that the
dominant taxa in them do not have an underlying latitudinal gradient in richness. In
either case, the lack of association between species richness
and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
between species richness and other properties is not being driven by underlying variation in
species richness, allowing us to more clearly assess effects of latitude on scaling with 
species richness and proportions of species in different trophic levels.

Scaling of links per species, generality, and vulnerability with species
richness varied strongly across ecosystem types. In estuarine, marine, and
terrestrial food webs scaling of each property varied little with latitude.
This is consistent with the idea that species' niche breadths do not vary
systematically with temperature and productivity but that the niche space
might be larger in species-rich communities~\citep{Davies2007}. In lake food
webs, in contrast, scaling of each property was much stronger in high-latitude
food webs. In stream food webs, scaling of links per species and vulnerability
varied little over latitude while scaling of generality was stronger in high-
latitude food webs. This means that species in trophical freshwater
communities gain fewer additional feeding links per additional species in the
web and is consistent with the hypothesis that greater stability in the
tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
specialists~\citep{}.

In lake food webs, species in tropical food webs also gained fewer predators,
and therefore fewer links overall. Conversely, for species in high-latitude
food webs numbers of predators, prey, and links per species all increased
rapidly with increasing species richness.
As there were proportionally fewer top predators in high-latitude lakes yet
generality, vulnerability, and links per species all increased more rapidly than
near the equator, it appears that high-latitude predators are more likely to be 
generalists. This may reflect prey switching as
different food sources become available in different seasons~\citep{}.

Surprisingly species in high-latitude stream food webs, while gaining many
additional prey species per additional species in the food web, did not
receive any more predators or links than species in low-latitude streams. 
This may be partly due to the increasing proportion of the food web made up of
basal resources at higher latitudes. If any additional species is more likely to
be a basal resource at high latitudes, it will have predators but no prey.
Combined with the potential for prey-switching between seasonal resources, this 
could account for the sharper increase in generality with increasing species richness
in high-latitude streams. Vulnerability and mean links per species, on the other hand,
increased at the same rate across latitude. [[Still working on why]]

@@

% Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
% types. This suggests that different types of food webs respond differently to differences in climate
% driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]

>>>>

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up 
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships in the estuarine,
marine, and terrestrial food webs, there were strong effects of latitude on
scaling relationships in the freshwater food webs. In these communities,
the latitude-niche breadth hypothesis appears to hold true while in other habitat
types niches appear to be broader in the tropics. These contrasting findings
indicate that it is important to account for habitat type when exploring gradients
in food-web structure.

\section*{Introduction}

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities~\citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes~\citep{mappaper}. These variables affect both the resources available and species' 
  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure~\citep{}.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.

@@

  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{,Vazquez2004}. 
  This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
  turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics \citep{Brown2004}
  may result in a broader niche space \citep{Davies2007} which could also sustain greater biodiversity even if niche 
  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
  supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
  richness \citep{Lappalainen2006,Krasnov2008,Slove2010}.

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialization (i.e., niche breadth) of species within food webs.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
  the ``latitude-niche breadth hypothesis''.

@@

  As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
  is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
  Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
  sets to form ``trophic species'' webs (e.g. ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
  is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
  species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
  of the dataset; in each case using the number of species ($S$) and 
  links ($L$) in each web to calculate the mean number of links per species ($Z$), mean generality 
  ($G$), and mean vulnerability ($V$) of the web. 
  The version of the dataset used did not qualitatively change the results, suggesting that
  the scaling relationships between species richness, other food-web properties, and latitude are very 
  similar whether or not redundant species are included. For simplicity, we present only
  the results for the original webs.

@@

  To determine whether there were latitudinal gradients in food-web structure,
  we first examined simple linear relationships between latitude and each of 
  species richness, links per species, generality, vulnerability, and proportions
  of basal resources, intermediate consumers, and top predators. We fit models of the form

@@

  \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
  latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
  variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
  marine, lake, and terrestrial networks with estuarine
  networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
  We next calculated the AIC
  of the maximal model as well as the AIC's of a suite of candidate simplified models identified
  using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
  Simplified models were obtained by
  systematically removing all possible combinations of terms from the full model.
  The best-fitting model was then determined to be the model with the fewest terms 
  where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
  and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
  model.

@@

  Next, we examined the form of the scaling relationship between each 
  property (links per species, generality, and vulnerability) and 
  species richness. The scaling relationship between links per species ($Z$) and 
  species richness ($S$) has been shown to be a power law \citep{Riede2010} of the form

@@

  Although scaling relationships between species richness and generality or
  species richness and vulnerability have not been explicitly examined (but see scaling 
  relationships for the standard devaitions of each property in \citet{Riede2010}), we expect that they will follow
  power laws similar to that of the relationship between species richness and links per species.
  This is because the links taken into account in calculating generality and vulnerability are subsets 
  of the total links included when calculating links per species. As with links per species, we explicitly 
  compared the error distributions of models for generality and vulnerability using
  both the power-law and logarithmic formulations. 
  In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
  species richness.

@@

  We then assessed the impact of latitude on the scaling relationships between species richness and 
  link density, generality, vulnerability. In the context of the scaling relationships above, note 
  that this implies that we aim to determine the effect of latitude on
  the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
  web property directly, we included a categorical variable for ecosystem type (stream, lake, 
  terrestrial, marine, or estuary), as well as interactions between food web type and latitude.

@@

  We were also interested in the ways that scaling relationships with species richness might
  be affected by changes to the distribution of species among trophic levels. To
  that end, we repeated all of the above analyses replacing species richness by
  proportion of basal resources, proportion of intermediate consumers,
  or proportion of top predators. All model fitting and model
  simplification procedures were identical to those described for species
  richness.

@@

  Contrary to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
  ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
  relationship was robust to the removal of three outliers (based on Cook's Distance). 
  There were also relationships between latitude and link density and latitude and vulnerability
  in stream food webs, but these trends were non-signficant after the removal of three outliers.
  Link density and vulnerability did not vary with latitude in any other ecosystem type.
  The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
  latitude in any ecosystem type.

  The relationships between latitude and the proportions of species at each trophic level were broadly similar
  to the relationship between latitude and species richness. 
  The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
  but did not vary with latitude in estuarine, marine, lake, or terrestrial 
  food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
  The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
  The proportion of top predators did not vary with latitude in 
  estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
  webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
  $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
  All of these trends were robust to the removal of outliers.

@@

  When considering the relationships between species richness or the proportions 
  of basal resources, intermediate consumers, or top predators and all response variables 
  (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
  lower AIC than did equation~(\ref{Power}). This indicates that the
  data support an assumption of multiplicative lognormal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an additive term on
  the logarithmic scale provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with species richness.

@@

  Link density, generality, and vulnerability each increased with increasing
  species richness (Fig.~\ref{S}; $\beta_0$=0.666, $p$\textless0.001; $\beta_0$=0.623,
  $p$\textless0.001; and $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine,
  marine, and terrestrial food webs this increase did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density; $\beta_{Latitude}$=-0.001, $p$=0.363 for generality;
  and $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability). In lake food webs, link density,
  generality, and vulnerability all increased more quickly towards the poles
  ($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
  $p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In
  stream food webs generality increased more rapidly towards the poles 
  ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\citep{}, intuitively one might suspect that any relationship
  between food-web properties such as generality might be due to the latitudinal
  gradient in species richness. In this dataset, however, we did not find
  overall latitudinal gradients in species richness, links per species, 
  generality, vulnerability, or the proportions of food webs accounted for by 
  basal resources, intermediate consumers, and top predators.

  The lack of latitudinal gradients in food-web properties in this dataset contrasts
  strongly with other studie~\citep{}. As numbers of species and links included in a food web
  vary strongly with sampling effort as well as with the underlying diversity of the study
  area, it is possible that the lack of latitudinal trends here is a result of researchers
  tending to expend similar amounts of sampling effort across studies. This could result in
  food webs describing species-rich tropical communities omitting more species and links
  than species-poor arctic communities. In addition, it is worth noting that gradients in
  species richness are generally measured for a single taxonomic group at a time~\citep{}.
  It is possible that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in richness. In
  either case, the lack of association between species richness
  and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
  between species richness and other properties is not being driven by underlying variation in
  species richness, allowing us to more clearly assess effects of latitude on scaling with 
  species richness and proportions of species in different trophic levels.

  Scaling of links per species, generality, and vulnerability with species
  richness varied strongly across ecosystem types. In estuarine, marine, and
  terrestrial food webs scaling of each property varied little with latitude.
  This is consistent with the idea that species' niche breadths do not vary
  systematically with temperature and productivity but that the niche space
  might be larger in species-rich communities~\citep{Davies2007}. Rather than
  niche space depending on temperature and productivity, it may be that species
  diversity itself affects the niche space available to species (although climate
  may affect speciation rates and therefore the diversity in a region~\citep()).

  Unlike other ecosystem types, in lake and stream food webs 
  the scaling of generality was stronger in higher-latitude food webs. 
  In lake food webs, this trend was echoed in the scaling relationships
  between species richness and links per species and vulnerability.
  This means that species in tropical freshwater
  communities gain fewer additional feeding links per additional species in the
  web and that species in tropical lakes also gain fewer predators, and fewer links
  in general, per additional species. These trends are consistent with the hypothesis
  that greater stability in the tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
  specialists, as has been observed in mutualist networks~\citep{}. Inhabitants of high-latitude
  freshwater communities may also be more generalist due to prey switching if they rely on a series
  of ephemeral prey such as maturing insect larvae~\citep{}.

@@

  Our results were consistent with the latitude-niche breadth hypothesis in estuarine, marine,
  and terrestrial communities but instead consistent with the hypothesis of greater specialization
  in the tropics in stream and lake food webs. This suggests that different mechanisms may structure
  food webs in different habitat types and that freshwater food webs in particular may be strongly
  affected by seasonal variation. In addition, different relationships between latitude and niche
  breadth in different habitat types goes some way towards explaining the equivocal support for
  the opposing hypotheses of~\citet{Brown2004} and ~\citet{Davies2007}; both have merit but appear
  to apply to different systems.
